\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Let's first define a biologically inspired trajectory inspired by eye movements. Indeed, these allow to dynamically actuate the axis of vision in the visual field of view. For instance, Saccades are rapid movements of the eyeball which reposition the center of vision. In humans, these are Very frequent (on average every 3 seconds [ ]). They are produced very rapidly C- 80ms) and the peak speed is proportional to the amplitude of the displacement (up to 600 deg/sec for a large saccade of 30deg of amplitude). At a more microscopic scale, the gaze moves with are incessant drift similar to a Brownian-like trajectory (Poletti 2015). To keep with the generality of the task, we defined eye movements using a form of Random walk (Engbert 211). This consists first to define a finite set of
possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set motion set of eye motions as the cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-speed=7 different speeds (see inset of fig : motion - task, a). Note that speeds are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Second, we define the trajectory as segments whose duration are drawn from a Poisson distribution with an average length of block-length = 20 ms - similar to a Levy flight. Finally, the trajectory is integrated by assuming 1/that speeds are uniformly and independently sampled from the set of different motions motion-set and 2/ that motion is uniform during a time segment. resulting instances are giving qualitatively similar trajectories as those observed for eye movements as observed for instance in humans (see figure fig : motion-task - a) .

@@

Once these eye-movement trajectories are simulated, we can use them on a visual scene. For this, we selected a database of 10 grayscale natural images which are typically used for studying tu statistics of natural images [olshausen 96]. Note that these are reprocessed in order to equalize the energy in each frequency band (that is, whitened). This process is known to occur as early as the retina-thalamic pathway [dan 1996]. These images are of size 512 × 512 and we will extract sub-images of
1281 128 which will be positionned around
the center of gaze at every time step (see
figure fig : motion -task - b).

We will discretize time in 1ms true bins and produce movies of duration N-T = 250 ms (that is, approximately corresponding to the mean duration between two saccades). To avoid border effects, we will position one draw of the full trajectory at random in image space such that the sub-image is translated using the position given by the trajectory at each time step. The translation is computed using a roll of coordinates in the horizontal and vertical dimensions, followed by a sub-pixel translation defined in Fourier space [Perrinet, 2015]. Note that the amplitude of the displacement is relative to the time bin and we defined speed such that a speed of V-1 corresponds to a motion of one pixel per frame (that is, per
time bin).

>>>>

Définissons au préalable une trajectoire biologiquement inspirée par les mouvements oculaires. En effet, ceux-ci permettent d'actionner dynamiquement le centre de vision dans le champ de vision. Par exemple, les saccades sont des mouvements rapides du globe oculaire qui repositionnent le centre de la vision vers des points d'interet. Chez l'homme, celles-ci sont très fréquentes (en moyenne toutes les 3 secondes [ ]). Elles sont produites très rapidement (environ 80ms) et la vitesse maximale est proportionnelle à l'amplitude du déplacement (jusqu'à 600 deg/sec pour une grande saccade de 30deg d'amplitude). À une échelle plus microscopique, le regard se déplace avec une dérive incessante similaire à une trajectoire de type brownien (Poletti 2015). Pour conserver toute la généralité de la tâche, nous avons défini les mouvements oculaires en utilisant une forme de marche aléatoire (Engbert 211). Cette démarche consiste d'abord à définir un ensemble défini de mouvements 2D possibles en coordonnées polaires. En nous basant sur la distribution des mouvements biologiques, nous l'avons simplifié en sélectionnant un ensemble de mouvements oculaires comme le produit cartésien de N-V-phi=8 directions de mouvement linéairement espacées et de N-Y-vitesse=7 vitesses différentes (voir encart de la fig : mouvement - tâche, a). Notez que les vitesses sont échantillonnées sur une échelle géométrique comprise entre $1/4$ et $v-speed_base = 4$. Ensuite, nous définissons la trajectoire comme des segments dont la durée est tirée d'une distribution de Poisson avec une longueur moyenne de bloc = 20 ms - similaire à un vol de Lévy. Enfin, la trajectoire est intégrée en supposant 1/que les vitesses sont échantillonnées de manière uniforme et indépendante à partir de l'ensemble de mouvements différents motion-set et 2/que le mouvement est uniforme pendant un segment de temps. Les instances résultantes donnent des trajectoires qualitativement similaires à celles observées pour les mouvements oculaires tels qu'observés par exemple chez les humains (voir figure fig : motion-task - a).

@@

Once these eye-movement trajectories are simulated, we can use them on a visual scene. For this, we selected a database of 10 grayscale natural images which are typically used for studying tu statistics of natural images [olshausen 96]. Note that these are reprocessed in order to equalize the energy in each frequency band (that is, whitened). This process is known to occur as early as the retina-thalamic pathway [dan 1996]. These images are of size 512 × 512 and we will extract sub-images of 1281 128 which will be positionned around the center of gaze at every time step (see figure fig : motion -task - b). We will discretize time in 1ms true bins and produce movies of duration N-T = 250 ms (that is, approximately corresponding to the mean duration between two saccades). To avoid border effects, we will position one draw of the full trajectory at random in image space such that the sub-image is translated using the position given by the trajectory at each time step. The translation is computed using a roll of coordinates in the horizontal and vertical dimensions, followed by a sub-pixel translation defined in Fourier space [Perrinet, 2015]. Note that the amplitude of the displacement is relative to the time bin and we defined speed such that a speed of V-1 corresponds to a motion of one pixel per frame (that is, per
time bin).
